---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

Libraries are loaded. The data is read and formatted for easy manipulation.

*Change the directory in the setwd() function to wherever activity.csv is placed.*

```{r}
library(ggplot2)
setwd("C:/Users/kiiiiibble/Desktop/Coursera - R Programming")
data<-read.csv("activity.csv")
data$date<-as.Date(data$date, format="%Y-%m-%d")
```

## What is mean total number of steps taken per day?

1. Get number of steps/day
```{r, echo=TRUE}
daystep<-aggregate(steps~date, data, sum)
```

2. Histogram
```{r, echo=TRUE}
hist(daystep$steps, main="HIstogram of total number of steps per day", xlab="Total number of steps per day")
```

3. Mean and Median
```{r, echo=TRUE}
mean(daystep$steps, na.rm=TRUE)
median(daystep$steps, na.rm=TRUE)
```

## What is the average daily activity pattern?

1. Get number of steps/interval
```{r, echo=TRUE}
intstep<-aggregate(steps~interval, data, mean, na.rm=TRUE)
```

2. Make time series plot
```{r, echo=TRUE}
ggplot(intstep, aes(interval, steps))+geom_line()
```

3. Get max interval
```{r, echo=TRUE}
intstep[intstep$steps==max(intstep$steps),]
```

## Imputing missing values

1. Number of NA
```{r, echo=TRUE}
sum(is.na(data$steps))
```

2. Put mean of steps in NA.
```{r, echo=TRUE}
data2<-data
data2$steps[is.na(data2$steps)]<-mean(data2$steps, na.rm=T)
ag2<-aggregate(steps~date, data2, sum)
hist(ag2$steps, main="Steps per day histogram", xlab="Steps per day")
```

3. New steps mean and median
```{r, echo=TRUE}
mean(ag2$steps)
median(ag2$steps)
```

3b. Old steps mean and median
```{r, echo=TRUE}
mean(daystep$steps)
median(daystep$steps)
```

Mean and median are more or less the same as the old.

## Are there differences in activity patterns between weekdays and weekends?

1. Make weekdays factor
```{r, echo=TRUE}
data2$date<-as.Date(data2$date, format="%Y-%m-%d")
data2$weekdays<-weekdays(data2$date)
for(i in 1:nrow(data2)){
        if(data2$weekdays[i]=="Saturday" || data2$weekdays[i]=="Sunday"){
                data2$weekdays[i]<-"Weekend"
        }
        else{
                data2$weekdays[i]<-"Weekday"
        }
}
```

2. Plot intervals vs. steps
```{r, echo=TRUE}
finaldata<-aggregate(steps~interval + weekdays, data=data2, mean)

ggx<-ggplot(finaldata, aes(interval, steps))+facet_grid(weekdays~.)+geom_line()
ggx
```
